DNSKEY Management

### 2012-12-10 paper/paper.tex
Some final typo fixes

Another type of TAR resides at the resolver: a statically configured
TAR stores keys locally at the resolver and hence does not require to issue an
additional query for keys when a new DNS request arrives. The
statically configured TAR may automatically poll keys asynchronously,
or may be just a bunch of manually configured trusted keys. As an
example of a statically configured TAR, we have
Vantages\footnote{\url{http://www.vantage-points.org/}}, a standalone
daemon, \cite{Osterweil09} which can poll keys from different
locations such as web pages, but also from other vantage resolvers. Of
course, the operator may also choose to add trusted keys manually.

@@

In Switzerland, for example, SWITCH plays both the roles of the registry and a registrar: other registrars also exist but one can purchase a domain name directly from SWITCH. Registries will generally delegate part or whole of the namespace registration managing to registrars\footnote{For example, one can also buy a .ch domain from \url{http://gandi.net}}

Registrants are also free to play the registry and registrar roles for their own sub-domains: groups, laboratories and associations within EPFL may apply for an \verb|epfl.ch.| sub-domain, like the LACAL and it's \verb|lacal.epfl.ch.| subdomain, for example.

@@

Enabling DNSSEC for a zone not isn't a \emph{do once and forget} operation, but requires additional coordination among the three R's. Let us see what managerial consequences arise, depending on if we cross or stay within certain administrative boundaries.

@@

\subsubsection{Multiple administrative domain}
DNSSEC's true challenges arise when we begin to consider several administrative entities (the three R's, mainly). As stated earlier, once the \verb|epfl.ch.| zone is signed it is easy for the school to sign \verb|www.epfl.ch.|. However, if the domain to be signed was \verb|epfl.ch.| or \verb|epfl.ae|, the school would have to deal with the entity or entities managing the TLD's (\verb|ch.|, managed by SWITCH, or \verb|ae.|\footnote{epfl.ae has been registered at 'Instra Corporation Pty Ltd', a registrar for the ae.}, respectively), which will have they own terms and conditions, which might very well vary among different registrars and TLD's.

@@

\begin{itemize}
\item[-] The transferred private key is not totally \emph{private} anymore, as now both the old and new service provider know it;
\item[-] Newly generated keys will require an update of the parent zone
\end{itemize}

>>>>

Another type of TAR resides at the resolver: a statically configured
TAR stores keys locally at the resolver and hence does not require to issue an
additional query for keys when a new DNS request arrives. The
statically configured TAR may automatically poll keys asynchronously,
or may be just a bunch of manually configured trusted keys. As an
example of a statically configured TAR, we have
Vantages\footnote{\url{http://www.vantage-points.org/}}, a standalone
daemon, \cite{Osterweil09} which can poll keys from different
locations such as web pages, but also from other Vantage resolvers. Of
course, the operator may also choose to add trusted keys manually.

@@

In Switzerland, for example, SWITCH plays both the roles of the registry and a registrar: other registrars also exist but one can purchase a domain name directly from SWITCH. Registries will generally delegate part or whole of the namespace registration management to registrars\footnote{For example, one can also buy a .ch domain from \url{http://gandi.net}}

Registrants are also free to play the registry and registrar roles for their own sub-domains: groups, laboratories and associations within EPFL may apply for an \verb|epfl.ch.| sub-domain, like the LACAL and its \verb|lacal.epfl.ch.| subdomain, for example.

@@

Enabling DNSSEC for a zone isn't a \emph{do once and forget} operation, but requires additional coordination among the three R's. Let us see what managerial consequences arise, depending on whether we cross or stay within certain administrative boundaries.

@@

\subsubsection{Multiple administrative domain}
DNSSEC's true challenges arise when we begin to consider several administrative entities (the three R's, mainly). As stated earlier, once the \verb|epfl.ch.| zone is signed it is easy for the school to sign \verb|www.epfl.ch.|. However, if the domain to be signed was \verb|epfl.ch.| or \verb|epfl.ae|, the school would have to deal with the entity or entities managing the TLDs (\verb|ch.|, managed by SWITCH, or \verb|ae.|\footnote{epfl.ae has been registered at 'Instra Corporation Pty Ltd', a registrar for the ae.}, respectively), which will have their own terms and conditions, that might very well vary among different registrars and TLDs.

@@

\begin{itemize}
\item[--] The transferred private key is not totally \emph{private} anymore, as now both the old and new service provider know it;
\item[--] Newly generated keys will require an update of the parent zone
\end{itemize}
